### 2019-02-19 sections/introduction.tex
contributions

\begin{itemize}
  \item
    We informally describe the essential concepts of task-oriented programming (\TOP).

@@

@@

  \item
    We have implemented \TOPHAT in iTasks to demonstrate that the first is a subset of the second.

  \item
    Using both informal and formal descriptions, we compare \TOP with multiple related works in areas,
    ranging from business process modelling languages, to process algebras and reactive programming frameworks.

>>>>

\begin{itemize}
  \item
    We describe the essential concepts of task-oriented programming.

@@

  \item
    Using both the essential concepts and the formal calculus, we compare \TOP with multiple related works, in areas ranging from business process modelling to process algebras and reactive programming.

@@

  \item
    %To create executable applications, we implemented \TOPHAT in iTasks.

    To create executable applications, we implemented the task layer of \TOPHAT in iTasks.
    This also demonstrates that the former is a subset of the latter.
